A Bayesian Nonparametric Approach to Neural Image Segmentation

### 2012-12-07 latex/submission.tex
started submission paper

\documentclass{article}

\begin{document}
\title{Weekly Paragraphs}
\author{Kui Tang}
\date{\today}
\maketitle
\section*{October 3, 2012}
To appear in: Related Work

All known connectomes reply on manual labels. White et al. published the first connectome of \emph{C. elegans} in 1986, marking axons, dendrites, and cell bodies in each frame and tracing the labels through frames \cite{White12111986}. More recent work uses computer assistance but fundamentally rely on a skilled human's identification of neural bodies \cite{Jarrell2012,Bock2011Roberts2011}.

@@

Semi-automated methods take small amounts of user input and then use the morphology of the image segment entire neural processes. Marker-Controlled watersheds \cite{Gonzales2008} is a classic technique, requiring the user to mark background and foreground. Roberts et al. \cite{Roberts2011} require a "scribble" inside a neuron on the first and last slices. At each slice, their algorithm segments the neuron by minimizing the anisotropic weighted total variation \cite{Unger2009} and propagating the inferred boundary as soft constraints for the next layer.

Unfortunately, current baseline speeds of computer-assisted manual tracing would take 10,000 person-years to construct a mouse cortical column, suggesting that fully automatic methods are necessary \cite{Briggman2006}.

>>>>

\documentclass{article}
\usepackage{natbib}

\begin{document}

\title{A Bayesian Nonparametric Approach to Neural Image Segmentation}

\author{Kui Tang and Frank Wood}
\date{\today}
\maketitle
\begin{abstract}
We develop a semi-supervised method to produce a probabilistic segmentation of neurons in electron micrograph images of brain tissue. Unlike previous approaches, which generate , BLAH BLAH. To do so, we model the distribution of neurons in an image as an infinite Gaussian mixture model. Each neuron's pixels are characterized by likelihood function that is a combination of multivariate Gaussian and naive Bayes features, while the total and location of neurons are inferred automatically, sidestepping many model-selection or hypothesis-combination difficulties in current approaches. Importantly, our model can incorporate both features derived directly from the data and features derived from the output of a supervised learner. Using data collected by Kasthuri et al., we show that our model can obtain plausible segmentations with no training data, while receiving a significant boost in its presence.

\section{Introduction}
A new branch of computational neuroscience, \emph{connectomics}, aims to reconstruct the physical location and circuit connectivity of the brain. Recent advances in electron microscopy have produced images of 10 nm in the lateral plane and 50 nm in the vertical plane, sufficient detail to capture most of even the smallest neural processes~\citep{Briggman2006}. The scale of the data is profound; the human brain is estimated to contain 100 billion neurons connected by up to a quadrillion synapses~\citep{Kasthuri2010}. Like the human genome project before, it is clear that automated methods are needed to map the connectome.

All published connectomes have been manually labelled. White et al. published the first connectome of \emph{C. elegans} in 1986, marking axons, dendrites, and cell bodies in each frame and tracing the labels through frames~\cite{White12111986}. More recent work uses computer assistance but fundamentally rely on a skilled human's identification of neural bodies~\cite{Jarrell2012,Bock2011Roberts2011}. Several authors have developed efficient semi-automated methods \cite{Roberts2011,Unger2009}. Unfortunately, current baseline speeds of computer-assisted manual tracing would still take 10,000 person-years to construct a mouse cortical column~\cite{Briggman2006}. Therefore, in the rest of the paper, we focus on automated techniques.

\section{Related Work}
Automated techniques generally begin by segmenting a 2D slice based on cell membrane boundaries---a highly distinctive feature.

\section{Methods}
We model an image as an infinite Gaussian mixture model. First proposed by Rasmussen~\citep{Rasmussen2000}, this model extends the classical finite Gaussian mixture model with $K$ classes to estimate $K$ automatically from the data.

\section{Results}

\section{Discussion}

\end{abstract}
\section*{October 3, 2012}
To appear in: Related Work

@@
